---
title: "Variation of needle phenolic content in Scots pine common garden trial"
output: html_notebook
#Trial overview: Seed from 21 native Scottish Scots pine populations were collected and reared in one of three nurseries: outdoors to the west (Inverewe; NW), outdoors to the east (Aberdeen; NE), and in a glasshouse to the east (Aberdeen; NG).After a few years, trees were transplanted to field sites in the west (Inverewe; FW), east (Glensaugh;FE), and south (Yair; FS). Here, we are only looking at trees from FS, all of which were raised in FG.
read data
```{r include = FALSE}
library(readr)
read.csv("Yair_Phenolics_Old_Complete.csv", header = TRUE)
data<-read.csv("Yair_Phenolics_Old_Complete.csv")
View(data)
```
character check
```{r include = FALSE}
str(data)
data$OriginForest<-as.factor(data$OriginForest)
```
plot
#This plot shows variation in total phenolic content, by origin zone/forest.
```{r}
library(ggplot2)
ggplot(data, aes(x = OriginForest, y = Total_Phenolics_in_Plant_material.mg.g., colour = Zone)) +
 geom_boxplot() + ggtitle("Total phenolic content by origin") +
 theme(axis.text.x = element_text(angle=45, vjust=1, hjust=1)) +
 theme(plot.title = element_text(hjust = 0.5)) +
 labs(y = "Total phenolic content mg/g", x = "Origin Forest", colour = "Zone") +
  facet_wrap(~ Zone, scales = 'free_x')
```
ccc 
